Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-04-22 Paper/manuscript_v2/manuscript_07_01.tex

%\section*{Acknowledgment}

@@

>>>>

\section*{Acknowledgements}

We thank Academy of Finland (grants 298742 and 313122), Finnish Center
for Artificial Intelligence, and Technology Industries of Finland
Centennial Foundation (grant 70007503; Artificial Intelligence for
Research and Development) for partial support of this research. We
also acknowledge the computational resources provided by the Aalto
Science-IT project.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
